### 2020-05-15 draft_ABP.tex
Updates from Overleaf

The ABHY construction of $\mathscr A_n$ is given by 
\[
	S_{[i,j]}=-C_{[i,j]} \,\,\text{ for all $i<j$,}\quad
	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
\]
where $C$'s are positive numbers. As first introduced in~\cite{Arkani-Hamed:2019vag}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice. For example, we can have the following mesh for ABHY realization of $\mathscr A_3$:  
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (-0.5,1) {$[0,2]$};
	\node at (1.35,1) {$[1,3]$};
	\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
where each diamond is labelled by $[i,j]$ of the top corner~\footnote{
It looks different with the usual mesh of $\mathscr A_n$~\cite{Arkani-Hamed:2019vag} where label of $c$ follows the left corner
in each diamond. This is because the mismatch of the correspondence of labels 
$X_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
}, and it gives
\begin{equation}\label{CinFA}
	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}\,.
\end{equation}
For each causal diamond, we have the Gauss law:
\[
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$

>>>>

The ABHY construction of $\mathscr A_n$ is given by 
\[
	S_{[i,j]}=-C_{[i,j]} \,\,\text{ for all $i<j$,}\quad
	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
\]
where $C$'s are positive numbers. As first introduced in~\cite{Arkani-Hamed:2019vag,Bazier-Matte:2018rat}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice. For example, we can have the following mesh for ABHY realization of $\mathscr A_3$:  
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (-0.5,1) {$[0,2]$};
	\node at (1.35,1) {$[1,3]$};
	\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
where each diamond is labelled by $[i,j]$ of the top corner~\footnote{
It looks different with the usual mesh of $\mathscr A_n$~\cite{Arkani-Hamed:2019vag} where label of $c$ follows the left corner
in each diamond. This is because the mismatch of the correspondence of labels 
$X_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
}, and it gives
\begin{equation}\label{CinFA}
	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}\,.
\end{equation}
For each causal diamond, we have the Gauss law:
\[
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$
